### 2017-12-11 readme.rmd
added dash

GTR+G and CAT-GTR+G are very similar models that were implemented in carefully controlled ways by Feuda *et al.* 2017, yet provide very different results. What will happen when we consider other similar, adjacent models? It isn't surprising when highly different models give different results, but when adding a single set of parameters gives a radically different result we should be skeptical that we have the final word in the problem under either model. The fact that the authors claim that "recoding is effective at reducing lineage-specific compositional heterogeneity", yet still get highly inconsistent results in different recoded analyses is also problematic. It is also interesting to note that authors of Feuda *et al.* declared another set of analyses ([Pisani *et al.* 2015](http://dx.doi.org/10.1073/pnas.1518127112)) to be the [nail in the coffin of Ctenophora sister](https://twitter.com/gwoerhe/status/671636958926499841) even though it did not use the recoding strategy that they now claim to be essential to testing these hypotheses. Such strong claims manufacture controversy where there is none and, in combination with moving goal posts, give the impression that the only consistent criterion they apply for detecting problems with analyses is finding that they support Ctenophora-sister.

>>>>

GTR+G and CAT-GTR+G are very similar models that were implemented in carefully controlled ways by Feuda *et al.* 2017, yet provide very different results. What will happen when we consider other similar, adjacent models? It isn't surprising when highly different models give different results, but when adding a single set of parameters gives a radically different result we should be skeptical that we have the final word in the problem under either model. The fact that the authors claim that "recoding is effective at reducing lineage-specific compositional heterogeneity", yet still get highly inconsistent results in different recoded analyses is also problematic. It is also interesting to note that authors of Feuda *et al.* declared another set of analyses ([Pisani *et al.* 2015](http://dx.doi.org/10.1073/pnas.1518127112)) to be the [nail in the coffin of Ctenophora-sister](https://twitter.com/gwoerhe/status/671636958926499841) even though it did not use the recoding strategy that they now claim to be essential to testing these hypotheses. Such strong claims manufacture controversy where there is none and, in combination with moving goal posts, give the impression that the only consistent criterion they apply for detecting problems with analyses is finding that they support Ctenophora-sister.
